AD Target Gene Report

### 2020-01-23 code/02-Master.Rmd
pre Mod7 final

---
title: "AD Target Gene Report"
author: "Jake Gockley"
date: "11/11/2019"
header-includes:
  - \usepackage{multicol}
  - \newcommand{\btwocol}{\begin{multicols}{2}}
  - \newcommand{\etwocol}{\end{multicols}}
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
opts_knit$set(root.dir = '../')
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
#webshot::install_phantomjs()
```

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "YAML_FILE"
config <- read_yaml(file=paste0('./',configuration))

@@

@@

Importing genelist `r thisFile` as `r config$genelisttype`
```{r GeneNames, eval=T, include=T}

@@

  org = 'hsa'
  host = 'grch37.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA

@@

}else{
  writeLines('Skipping IGAP based Model and Gene-Ranking: User specified module 1 not included in <Config>.yaml ')
}

@@

  source('modules/02-DiffExp_module.R')

}else{
  writeLines('Skipping Differential Expression based Model and Gene-Ranking: User specified module 2 not included in <Config>.yaml ')
}

@@

>>>>

---
title: "AD Target Gene Report"
author: "Jake Gockley"
date: "11/11/2019"
header-includes:
  - \usepackage{multicol}
  - \newcommand{\btwocol}{\begin{multicols}{2}}
  - \newcommand{\etwocol}{\end{multicols}}
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
knitr::opts_knit$set(root.dir = config$filedir )
print(getwd())
#webshot::install_phantomjs()
```

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable
configuration <- "YAML_FILE"
config <- read_yaml(file=paste0('./',configuration))

@@

#Create Synapse Run Folder and retrieve parentID
CODE <- syn_temp$store(synapseclient$Folder(name = config$runID, parentId = config$parentID))

foo <- syn_temp$getChildren('syn21532475')
Temp <- reticulate::iterate(foo, simplify = F)
for( i in 1:length(Temp) ){
  if( Temp[[i]]$name == config$runID ){
    RunParent <- Temp[[i]]$id
  }else{
  }
}

@@

Importing genelist `r config$genelistfile` as `r config$genelisttype`
```{r GeneNames, eval=T, include=T}

@@

  org = 'hsa'
  host = 'grch38.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

@@

Tab <- GeneData( Genes, config$genelisttype )
#Trans used as raw for module 7
Trans <- Tab
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA

@@

}else{
  writeLines( paste0('Skipping IGAP based Model and Gene-Ranking: User specified module 1 not included in ', config$name) )
}

@@

  source('code/modules/02-DiffExp_module.R')

}else{
  writeLines( paste0('Skipping Differential Expression based Model and Gene-Ranking: User specified module 2 not included in ', config$name) )
}

@@

```{r Module3, eval = T, include=T}
if( 3 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Proteomic Expression evidence')

  source('code/modules/03-DiffProt_module.R')

}else{
  writeLines( paste0('Skipping Differential Proteomic Expression based Model and Gene-Ranking: User specified module 3 not included in ', config$name) )
}

```{r Module4, eval = T, include=T}
if( 4 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by eQTL evidence')

  source('code/modules/04-eQTL_module.R')

}else{
  writeLines( paste0('Skipping eQTL based Model and Gene-Ranking: User specified module 4 not included in ', config$name) )
}

```{r Module5, eval = T, include=T}
if( 5 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Coexpression Module evidence')

  source('code/modules/05-CoExp_module.R')

}else{
  writeLines( paste0('Skipping Coexpression Module based Model and Gene-Clustering: User specified module 5 not included in ', config$name) )
}

```{r Module6, eval = T, include=T}
if( 6 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Module Cell-Type Enrichments evidence')

  source('code/modules/06-CellType_module.R')

}else{
  writeLines( paste0('Skipping Coexpression Module based Model and Gene-Clustering: User specified module 6 not included in ', config$name) )
}

```{r Module7, eval = T, include=T}
setwd( config$filedir )
if( 7 %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by Differential Expression evidence')

  source('code/modules/07-Coexpression.R')

}else{
  writeLines( paste0('Skipping Partial Coexpression Analysis: User specified module 7 not included in ', config$name) )
}

### 2020-01-23 code/03-Run.Rmd
pre Mod7 final

---
title: "AD Target Gene Report"
author: "Jake Gockley"
date: "11/11/2019"
header-includes:
  - \usepackage{multicol}
  - \newcommand{\btwocol}{\begin{multicols}{2}}
  - \newcommand{\etwocol}{\end{multicols}}
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
opts_knit$set(root.dir = '../')
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
#webshot::install_phantomjs()
```

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(file=paste0(configuration))

@@

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
```

>>>>

---
title: "AD Target Gene Report"
author: "Jake Gockley"
date: "11/11/2019"
header-includes:
  - \usepackage{multicol}
  - \newcommand{\btwocol}{\begin{multicols}{2}}
  - \newcommand{\etwocol}{\end{multicols}}
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readr)
library(biomaRt)
library(knitr)
library(kableExtra)
library(tidyverse)
library(grid)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(yaml)
knitr::opts_knit$set(root.dir = config$filedir )
print(getwd())
#webshot::install_phantomjs()
```

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(file=paste0('./',configuration))

@@

Tab <- GeneData( Genes, config$genelisttype )
#Trans used as raw for module 7
Trans <- Tab
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA

for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}
```
